\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Expand slightly on why we don't use meek more often.

\item{\bfseries Financial constraints}: Leveraging harder-to-block \texttt{meek} bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
\end{itemize}

>>>>

\item{\bfseries Financial constraints}: The \texttt{meek} bridges are especially effective at avoiding censorship: they are harder to block without imposing significant collateral damage (e.g., to Amazon Web Services) and are harder to detect through passive monitoring~\cite{fifield2015blocking}.
Leveraging these harder-to-block bridges can help users in heavily censored environments, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
\end{itemize}
